```
---
title: "Regression Analysis"
author: Allison Sharr
date: "December 7, 2024"
output: html_document
---
```

# Set Up
A list of the libraries required to run through the code whilst conducting analysis.
```{r libraries}
library(tidyverse)
library(janitor)
```

# Data
```{r load data}
#State
base1 <- read.csv("../../MMG_State.csv") |>
        clean_names()
#County
base2 <- read.csv("../../MMG_County.csv") |>
        clean_names()

#District
base3 <- read.csv("../../MMG_Districts.csv") |>
        clean_names()
```

```{r clean data}
#State
recent <- base1 |>
          select(-23:-30) |>
          mutate(x_fi_low_threshold = ifelse(year %in% 2019:2022, 
                                             x_fi_snap_threshold, 
                                             x_fi_low_threshold),
                 low_threshold_type = ifelse(year %in% 2019:2022, 
                                             "SNAP", 
                                             low_threshold_type),
                 x_fi_high_threshold = ifelse(year %in% 2019:2022, 
                                              x_fi_snap_threshold_1, 
                                              x_fi_high_threshold),
                 high_threshold_type = ifelse(year %in% 2019:2022, 
                                              "SNAP", 
                                              high_threshold_type)) |> 
          select(-20,-22) |> 
          select(1:8,20,9:19)
#County
#District
```

```{r}
model <- lm(data = recent, 
            food_insecurity_rate ~ state + year + 
                                   x_of_food_insecure_persons + 
                                   x_fi_low_threshold + x_fi_high_threshold +
                                   cost_per_meal + 
                                   weighted_annual_food_budget_shortfall)
summary(model)
```

### Step-Wise Regression
```{r step-wise regression analysis, echo=FALSE}
model <- lm(data = recent, 
            #food_insecurity_rate ~ state) 
              # R2 = 0.5835
            #food_insecurity_rate ~ state + year)
              # R2A = 0.8357
            #food_insecurity_rate ~ state + year + 
                                   #x_of_food_insecure_persons) 
              # R2A = 0.8856
            #food_insecurity_rate ~ state + year +
                                   #x_of_food_insecure_persons + 
                                   #x_fi_low_threshold) 
              # R2A = 0.8859
            #food_insecurity_rate ~ state + year +
                                   #x_of_food_insecure_persons +
                                   #x_fi_low_threshold + x_fi_high_threshold)
              # R2A = 0.8857
            #food_insecurity_rate ~ state + year +
                                   #x_of_food_insecure_persons +
                                   #x_fi_low_threshold + x_fi_high_threshold + 
                                   #cost_per_meal)
              # R2A = 0.9021
            food_insecurity_rate ~ state + year +
                                    x_of_food_insecure_persons +
                                    x_fi_low_threshold + x_fi_high_threshold + 
                                    cost_per_meal + 
                                    weighted_annual_food_budget_shortfall)
              # R2A = 0.9059
summary(model)
```

#Relationship Exploration
  #state
  model <- lm(data = recent, 
              food_insecurity_rate ~ state)
    #Check Assumptions
          #QQ Plot
          ggplot(mapping = aes(sample = model$residuals)) +
            stat_qq() + 
            stat_qq_line() +
            labs(title = "State",
                 x = "",
                 y = "Residuals")
          #Scatter Plot
          ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) +
            geom_point() +
            geom_hline(yintercept = 0) +
            labs(title = "State",
                 x = "Fitted Values",
                 y = "Residuals")
      #1. Equal Variance
      #2. Normality
      #3. Linearity 
      #4. Independence
  #year
  model <- lm(data = recent, 
              food_insecurity_rate ~ year)
    #Check Assumptions
          #QQ Plot
          ggplot(mapping = aes(sample = model$residuals)) +
            stat_qq() + 
            stat_qq_line() +
            labs(title = "State",
                 x = "",
                 y = "Residuals")
          #Scatter Plot
          ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) + 
            geom_point() +
            geom_hline(yintercept = 0) +
            labs(title = "Year",
                 x = "Fitted Values",
                 y = "Residuals")
  #x_of_food_insecure_persons
  model <- lm(data = recent, 
              food_insecurity_rate ~ x_of_food_insecure_persons) 
    #Check Assumptions
            #QQ Plot
            ggplot(mapping = aes(sample = model$residuals)) +
              stat_qq() + 
              stat_qq_line() +
              labs(title = "State",
                   x = "",
                   y = "Residuals")
            #Scatter Plot
            ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) + 
              geom_point() +
              geom_hline(yintercept = 0) +
              labs(title = "Number of Food Insecure Persons",
                   x = "Fitted Values",
                   y = "Residuals")
  #x_fi_low_threshold
  model <- lm(data = recent, 
              food_insecurity_rate ~ x_fi_low_threshold)
    #Check Assumptions
          #QQ Plot
          ggplot(mapping = aes(sample = model$residuals)) +
            stat_qq() + 
            stat_qq_line() +
            labs(title = "State",
                 x = "",
                 y = "Residuals")
          #Scatter Plot
          ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) + 
            geom_point() +
            geom_hline(yintercept = 0) +
            labs(title = "FI Low Threshold",
                 x = "Fitted Values",
                 y = "Residuals")
  #x_fi_high_threshold
  model <- lm(data = recent, 
              food_insecurity_rate ~ x_fi_high_threshold)
    #Check Assumptions
          #QQ Plot
          ggplot(mapping = aes(sample = model$residuals)) +
            stat_qq() + 
            stat_qq_line() +
            labs(title = "State",
                 x = "",
                 y = "Residuals")
          #Scatter Plot
          ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) + 
            geom_point() +
            geom_hline(yintercept = 0) +
            labs(title = "FI High Threshold",
                 x = "Fitted Values",
                 y = "Residuals")
  #cost_per_meal
  model <- lm(data = recent, 
              food_insecurity_rate ~ cost_per_meal)
    #Check Assumptions
          #QQ Plot
          ggplot(mapping = aes(sample = model$residuals)) +
            stat_qq() + 
            stat_qq_line() +
            labs(title = "State",
                 x = "",
                 y = "Residuals")
          #Scatter Plot
          ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) + 
            geom_point() +
            geom_hline(yintercept = 0) +
            labs(title = "Cost per Meal",
                 x = "Fitted Values",
                 y = "Residuals")
  #weighted_annual_food_budget_shortfall
  model <- lm(data = recent, 
              food_insecurity_rate ~ weighted_annual_food_budget_shortfall)
    #Check Assumptions
          #QQ Plot
          ggplot(mapping = aes(sample = model$residuals)) +
            stat_qq() + 
            stat_qq_line() +
            labs(title = "State",
                 x = "",
                 y = "Residuals")
          #Scatter Plot
          ggplot(mapping = aes(x = model$fitted.values, y = model$residuals)) + 
            geom_point() +
            geom_hline(yintercept = 0) +
            labs(title = "Weighted Annual Food Budget Shortfall",
                 x = "Fitted Values",
                 y = "Residuals")